A mechanization of semi-simplicial and semi-cubical sets in the calculus of inductive constructions

### 2022-10-11 paper/paper.tex
paper: minor polish

The characterization of $\framep[n]$ and $\filler[n]$ can be obtained by a recursive definition reminiscent from parametricity translation \cite{reynolds72}: a $\filler[n+1]$ is obtained by taking two $\filler[n]$ plus a third $\filler[n]$ connecting the two full $\filler[n]$. Since it connects $\filler[n]$, the third $\filler[n]$ is actually a $\filler[n]$ over lines, so it is shifted by one relatively to the underlying relational structure. Let us write $\filler[n][p]$ for a $\filler[n - p]$ over points which are $\filler[p]$. Working informally, we thus have the equation:

@@

The full explicit definition shall be given in the next sections but, to give an idea, let us show the structure of an $n$-filler for the first three dimensions.

A full $2$-filler is made of two full $1$-fillers connected by a lifted $1$-filler made of two lines connecting the former points and a square connecting the former lines:

>>>>

The characterization of $\framep[n]$ and $\filler[n]$ can be obtained by a recursive definition reminiscent from parametricity translation \cite{reynolds72}: a $\filler[n+1]$ is obtained by taking two $\filler[n]$ plus a third $\filler[n]$ connecting the two $\filler[n]$. Since it connects $\filler[n]$, the third $\filler[n]$ is actually a $\filler[n]$ over lines, so it is shifted by one relatively to the underlying relational structure. Let us write $\filler[n][p]$ for a $\filler[n - p]$ over points which are $\filler[p]$. Working informally, we thus have the equation:

@@

The full explicit definition shall be given in the next sections but, to give an idea, let us show the structure of a $\filler[n]$ for the first three dimensions.

A $\filler[2]$ is made of two $\filler[1]$ connected by a lifted $\filler[1]$ made of two lines connecting the former points and a square connecting the former lines.
